---
title: "Adults-2023"
author: "Solym Manou-Abi"
date: "2023-12-30"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# REQUIRED PACKAGE
```{r warning=FALSE, message=FALSE}
source("shift_grid.R")
source("Utilities.R")
source("AdultDataCleaning.R")



```{r}
adultdata00 <- read_excel("./2. Adult_results/CleanedData/capture_adult.xlsx") %>% 
  mutate(Week = week(Installation_date)) %>% filter(Year > 2017)
df <- adultdata00
adultdata00 %>% 
  ggplot(aes(Longitude, Latitude)) + geom_point()
```


#Data cleaning


```{r}
adultdata00_sf <- st_as_sf(df, coords = c("Longitude", "Latitude"),
                       crs= "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")

adultdata00_sf <- st_transform(adultdata00_sf, crs = st_crs(myt_map))
adultdata00_sf <- bind_cols(adultdata00_sf, st_coordinates(st_centroid(adultdata00_sf$geometry)))


intersections <- st_intersects(adultdata00_sf$geometry, myt_map)
adultdata00_sf$Village_intersect <- myt_map$village[as.integer(intersections)]
adultdata00$Village_intersect <- myt_map$village[as.integer(intersections)]

id_out <- which(is.na(adultdata00$Village_intersect))
villages <- unique(adultdata00$Village[id_out])

# adultdata00$Village_intersect[id_out]
# adultdata00$Latitude[id_out]
# adultdata00$Longitude[id_out]

# for (i in 1:4){
#   cat("i =", i, "\n")
#   x <- adultdata00$Latitude[adultdata00$Village == villages[[i]] & is.na(adultdata00$Village_intersect)]
#   y <- mean(adultdata00$Latitude[adultdata00$Village == villages[[i]] & !is.na(adultdata00$Village_intersect)])
#   
#   # id of the far off point
#   
#   
#   xx <- adultdata00$Longitude[adultdata00$Village == villages[[i]] & is.na(adultdata00$Village_intersect)]
#   yy <- mean(adultdata00$Longitude[adultdata00$Village == villages[[i]] & !is.na(adultdata00$Village_intersect)])
#   
#   if(max(abs(x-y)) < 0.01){
#     next
#   } else {
#     adultdata00$Latitude[adultdata00$Village == villages[[i]] & is.na(adultdata00$Village_intersect)] <- y
#   }
#   
#   if(max(abs(xx-yy)) < 0.01){
#     next
#   } else {
#     adultdata00$Longitude[adultdata00$Village == villages[[i]] & is.na(adultdata00$Village_intersect)] <- yy
#   }
# }
# 
# adultdata00 %>% 
#   ggplot(aes(Longitude, Latitude, col = (!is.na(Village_intersect)))) + geom_point()
```


```{r}
calibrate_cordinates <- function(df, max_lon = 45.3, max_lat = -12.6, col = "Village", index_out){
  # list of communes names that are out of the range
  
  
  vil_names_lon <- df %>% 
    filter(Longitude >= max_lon) %>% 
    dplyr::select(all_of(col)) %>% as.matrix() %>% as.character() %>% unique()
    
  vil_names_lat <- df %>% 
    filter(Latitude >= max_lat) %>% 
    dplyr::select(all_of(col)) %>% as.matrix() %>% as.character() %>% unique()
    
  for (i in 1:length(vil_names_lon)){
    # coordinates that are in the range from the same village
    avg_coord <- mean(df$Longitude[df$Longitude < max_lon & df[[col]] == vil_names_lon[[i]]], na.rm = TRUE)
    df$Longitude[df$Longitude >= max_lon & df[[col]] == vil_names_lon[[i]]] <- avg_coord
  }
    
  for (i in 1:length(vil_names_lat)){# coordinates that are in the range from the same village
    avg_coord <- mean(df$Latitude[df$Latitude < max_lat & df[[col]] == vil_names_lat[[i]]], na.rm = TRUE)
    df$Latitude[df$Latitude >= max_lat & df[[col]] == vil_names_lat[[i]]] <- avg_coord
  }
  
  df
}

adultdata00 <- calibrate_cordinates(adultdata00)

adultdata00 %>% 
  ggplot(aes(Longitude, Latitude, col = (!is.na(Village_intersect)))) + geom_point()
```



### Adult mosquito daily data as we did with egg data
```{r}
# adult mosquito data
with_village = FALSE

if (with_village){
  adultdata0 <- adultdata00 %>% 
    filter(Year > 2017) %>% 
    group_by(Year, Date = Collection_date, commune = Commune, village = Village, Longitude, Latitude) %>% 
    summarise(Num_adults = sp_func(Nb, mean), .groups = "drop") %>% 
    mutate(Week = week(Date), Year = as.factor(Year))
} else {
  adultdata0 <- adultdata00 %>% 
    filter(Year > 2017) %>% 
    group_by(Year, Date = Collection_date, commune = Commune) %>% 
    summarise(Num_adults = sp_func(Nb, mean), .groups = "drop") %>% 
    mutate(Week = week(Date), Year = as.factor(Year))
}
  
  
head(adultdata0)
# all communes
all_communes <- myt_map$commune %>% unique()
# date range to get daily data
date_range <- daterange(start_date = min(adultdata0$Date), end_date = max(adultdata0$Date))
head(date_range)
# adding commune to data_range
date_com <- get_daily_data(date_range, all_communes)
```


```{r}
adultdata00_sf <- st_as_sf(adultdata00, coords = c("Longitude", "Latitude"),
                       crs= "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")

adultdata00_sf <- st_transform(adultdata00_sf, crs = st_crs(myt_map))
adultdata00_sf <- bind_cols(adultdata00_sf, st_coordinates(st_centroid(adultdata00_sf$geometry)))

myt_map_commune %>% 
  ggplot() + geom_sf() + 
  geom_point(data = adultdata00_sf %>% mutate(Outlier = !is.na(Village_intersect)), 
             aes(X, Y, col = Outlier)) + theme_map()
```

* Adding the weight variable
```{r}
weight <- adultdata00 %>% 
  group_by(Year, Commune, Village, Week) %>% 
  summarise(weight = 100*sum(!is.na(Nb))/nrow(adultdata00), .groups = "drop")

adultdata00 <- adultdata00 %>% left_join(weight, by = c("Year", "Commune", "Village", "Week"))
```



```{r}
myt_map_commune %>% filter(commune == "Koungou") %>% ggplot() + geom_sf() + 
  geom_point(data = adultdata00_sf %>% filter(Commune == "KOUNGOU", Year == 2018),
             aes(X, Y, col = Nb)) + #, col = (!is.na(Num_eggs)) %>% factor()
  scale_color_gradient2(low = "green", mid = "yellow", high = "red") + 
  facet_wrap(~Week) + theme_minimal()
```


### The table of climate data with all the constructed columns (bycom)
```{r}
bycom <- read_excel("./1. egg_Resuls/CleanedData/bycom.xlsx") %>% 
  mutate(Year = factor(Year)) %>% 
  dplyr::select(-contains("_Q"))
head(bycom)
```

### Merging data
```{r}
adultdata <- adultdata0 %>% 
  full_join(date_com, by = c("Date", "commune", "Year", "Week")) %>% 
  arrange(commune) %>% 
  left_join(bycom, by = c("commune" = "NAME", "Date" = "DATE", "Year"))

head(adultdata)

# adultdata_sf <- st_as_sf(adultdata, coords = c("Longitude", "Latitude"),
#                        crs= "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
# 
# adultdata_sf <- st_transform(adultdata_sf, crs = st_crs(myt_map))
# adultdata_sf <- bind_cols(adultdata_sf, st_coordinates(st_centroid(adultdata00_sf$geometry)))

# adding number of eggs as a covariable
# la table des dechets
waste_data <- read_excel("./1. Egg_Resuls/CleanedData/cleaned_eggData_with_climatedf_wastedf.xlsx") %>% dplyr::mutate(Year = as.factor(Year))

eggdata <- read_excel("./1. Egg_Resuls/CleanedData/eggdata_updated.xlsx") %>% 
  mutate(Date = as.Date(Date)) %>% # soustraire
  dplyr::select(Year, Date, commune, Week, Num_eggs = Num_eggs_IDW) %>% 
  mutate(Year = factor(Year), Week = week(Date))

adultdata1 <- adultdata %>% 
  mutate(Date = as.Date(Date)) %>% #left_join(waste_data, by = c("Year", "Date", "commune", "Week")) %>%  # %>% left_join(eggdata, by = c("Year", "Date", "commune", "Week")) %>% 
  filter(!is.na(RR))

dim(adultdata)
dim(adultdata1) # difference due au filter(!is.na(RR))
```

### Ajout de la variable poids
```{r}
# weight <- adultdata1 %>% 
#   group_by(Year, commune, Week) %>% 
#   summarise(weight = sum(!is.na(Num_adults), na.rm = TRUE)/n(), .groups = "drop") %>% 
#   filter(commune == "KOUNGOU", Year %in% 2019:2021)
# 
# adultdata1 <- adultdata1 %>% left_join(weight, by = c("Year", "commune", "Week"))
```


## distribution du nombre de moustique par an
```{r}
adultdata1 %>% filter(!is.na(Num_adults)) %>% 
  ggplot(aes(commune, Num_adults, col = commune)) + geom_boxplot() + 
  facet_wrap(~Year, scales = "free_x", nrow = 1) + theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggsave("./2. Adult_results/boxplots.png")
```


## Distribution de donnees par commune et par semaine et annee
```{r}
p <- adultdata1 %>% 
  filter(Year %in% 2018:2021) %>% 
  group_by(Year, commune, Week) %>% 
  # Number of observations per week
  summarise(obs_num = sum(!is.na(Num_adults)), .groups = "drop") %>% #filter(commune == "KOUNGOU") %>% 
  ggplot(aes(as.factor(Week), obs_num, fill = commune)) + geom_col() + 
  xlab("Week") + ylab("Week observation frequency") + 
  facet_wrap(~Year, scales = "free", ncol = 1) +
  theme_minimal()

plotly::ggplotly(p)

# frequency table
the_table <- adultdata1 %>% 
  filter(Year %in% 2018:2021, !is.na(Num_adults)) %>% count(Year, commune, Week) %>% 
  spread(key = Year, value = n) %>% 
  flextable() %>% autofit() %>% theme_box() %>% merge_v(j = 1)

the_table %>% 
  save_as_docx(path = "./2. Adult_results/weely_frequency_tables.docx")
print(the_table)


# number of weeks where data were collected in a given commune
# frequency table
week_num <- adultdata1 %>% 
  filter(Year %in% 2018:2021, !is.na(Num_adults)) %>% count(Year, commune) %>%
  spread(key = Year, value = n) %>% 
  flextable() %>% autofit() %>% theme_box() %>% merge_v(j = 1)

week_num %>% 
  save_as_docx(path = "./2. Adult_results/number_of_weeks_by_year_commune.docx")
print(week_num)


# les communes representees par ans
communes_year <- adultdata1 %>%
  filter(Year %in% 2018:2021, !is.na(Num_adults)) %>% group_by(Year) %>% 
  summarise(communes = paste0(sort(unique(commune)), collapse = " - "), 
            `Count` = length(unique(commune)), `% obs.` = n()) %>% 
  mutate(`% obs.` = round(100*`% obs.`/sum(`% obs.`), 2)) %>%
  flextable() %>% autofit() %>% width(j=2, width = 3) %>% theme_box()

communes_year %>% 
  save_as_docx(path = "./2. Adult_results/number_of_communes_by_year.docx")
print(communes_year)


# table for Koungou
adultdata1 %>% filter(commune == "KOUNGOU", !is.na(Num_adults)) %>%  
  group_by(commune, Year) %>% 
  summarise(Nb_week  = length(unique(Week)), nb_obs = n(),
            .groups = "drop") %>% 
  flextable() %>% autofit() %>% theme_box() %>% merge_v(j = 1)
```




## Models
```{r}
years <- c(2018, 2019, 2021)
id_train <- adultdata1$Year %in% years & !is.na(adultdata1$Num_adults)
numadult <- adultdata1 %>% dplyr::select(Num_adults)

adultdata1_minmaxed <- adultdata1 %>%
  mutate(Year = as.numeric(as.character(Year))) %>%
  mutate_if(is.numeric, list(min_max)) %>% 
  dplyr::select(-Rained, -Date, -Date.y) %>% 
  mutate(Num_adults = ceiling(numadult$Num_adults))

data_allcom <- adultdata1_minmaxed[id_train,]


# model lasso
trainControl <- trainControl(method = "cv", number = 5)
lasso_reg <- train(Num_adults ~. -commune -Year, data = data_allcom,
                   method = "glmnet", family = poisson(), trControl = trainControl)
lasso_reg

v_imp <- varImp(lasso_reg)
plot(v_imp)

VIMP <- v_imp$importance %>% #filter(Overall > 1) %>% 
  arrange(desc(Overall)) %>% 
  rownames_to_column("Variable") %>% 
  mutate(Overall = round(Overall, 2))

VIMP %>% flextable() %>% 
  autofit() %>% theme_box()


write.xlsx(VIMP, "./1. egg_Resuls/VIM.xlsx")

VIMP %>% 
  filter(Overall > 0) %>% 
  ggplot(aes(reorder(Variable, Overall), Overall)) + geom_col() + 
  theme_minimal() + xlab("Variable") + 
  theme(axis.text.x = element_text(angle = 80, vjust = 0.5)) 
ggsave("./2. Adult_results/variable_importance.png")
ggsave("./2. Adult_results/variable_importance.pdf")


data_allcom$fitted <- fitted(lasso_reg)
data_allcom %>% 
  ggplot(aes(Num_adults, fitted, col = commune)) + geom_point() + 
  xlab("observed") + theme_minimal() + 
  ggtitle("Fitted vs observed", subtitle = "for all commune")
ggsave("./2. Adult_results/observed_vs_fitted_lasso.png")
ggsave("./2. Adult_results/observed_vs_fitted_lasso.pdf")

variables <- VIMP$Variable[VIMP$Overall > 0]

formule <- Num_adults ~RRcum_5 + MRR35 + MNDwtRR_14 + TN + MNDwRR_28 + Week + MNDwRR_21 + MNDwRR_6 + MTX_35 + MRR5 + MNDwtRR_35 + MTX_3 + MNDwRR_2 + MNDwtRR_2
lasso_vimp <- train(formule, data = data_allcom,
                   method = "glmnet", family = poisson(), trControl = trainControl)

lasso_vimp

v_imp <- varImp(lasso_vimp)
plot(v_imp)

VIMP <- v_imp$importance %>% #filter(Overall > 1) %>% 
  arrange(desc(Overall)) %>% 
  rownames_to_column("Variable") %>% 
  mutate(Overall = round(Overall, 2))

VIMP %>% flextable() %>% 
  autofit() %>% theme_box()


VIMP %>% 
  filter(Overall > 0) %>% 
  ggplot(aes(reorder(Variable, Overall), Overall)) + geom_col() + 
  theme_minimal() + xlab("Variable") + 
  theme(axis.text.x = element_text(angle = 80, vjust = 0.5)) 
# paste0(paste0("Num_adults ~"), paste0(variables, collapse = " + "))
variables2 <- VIMP$Variable[VIMP$Overall > 0]
paste0(paste0("Num_adults ~"), paste0("s(", c(variables2, "Year"), ")", collapse = " + "))
```
##Correlation test (Person) 

```{r}
#View(data_allcom)
outcome=data_allcom$Num_adults
cor(outcome, data_allcom$Y)
```

```{r}
variables2
```


Random forest model
```{r}
# # random forests
# rf_reg <- train(formule, data = data_allcom,
#                    method = "xgbTree", trControl = trainControl)
# rf_reg
# 
# # variable importance
# varImp(rf_reg) %>% plot()
```

## Models
#nb() pour negative binomial
#poisson() pour Poisson 
```{r}
k = 10
# + s(MTX_35, k = k) + s(RRcum_5, k = k)
fmla <- Num_adults ~ s(MTX_35, Week, k = k) + s(RRcum_5, Week, k = k) + s(MNDwRR_6, k = 6) + MRR35 + s(MTX_3, k = k) + s(MNDwtRR_14, k = k) + s(MNDwRR_28, k = 10) + s(MNDwRR_21, k = k) + TN + s(MRR5, k = k) + s(MNDwtRR_35, k = k) + s(MNDwRR_2, k=3) #+ waste_number

fmla2 <- Num_adults ~ s(MTX_35, MRR35, k = k) + s(RRcum_5, Week, k = k) + s(MNDwRR_6, k = 6) + s(MTX_3, k = k) + s(MNDwtRR_14, k = k) + s(MNDwRR_28, k = 10) + s(MNDwRR_21, k = k) + TN + s(MRR5, k = k) + s(MNDwtRR_35, k = k) + s(MNDwRR_2, k=3) + s(Year, bs = "re")

# fmla2 <- Num_adults ~ s(MTX_35, MRR35, k = k) + s(MTX_35, Week, k = k) + s(RRcum_5, Week, k = k) + s(MNDwRR_6, k = 6) + s(MNDwtRR_14, k = k) + s(MNDwRR_28, k = 10) + s(MNDwRR_21, k = k) + TN

# fmla_sp <- Num_adults ~s(RRcum_5) + s(MTX_35) + s(MTX_3) + MRR35 + TN + s(MNDwRR_28) + s(MNDwtRR_14) + s(MNDwRR_21) + s(MRR5) + s(MNDwtRR_35) + s(Week) + s(MNDwRR_2) + Year

gam_toutes <- mgcv::gam(fmla, data = data_allcom, family = poisson(), method = "REML", select = TRUE)
gam_toutes2 <- mgcv::gam(fmla2, data = data_allcom, family =poisson(), method = "REML")
summary(gam_toutes)
summary(gam_toutes2)
coef(gam_toutes)

lapply(data_allcom[variables2], function(x) length(unique(x))) %>% unlist()

# cor_pmat(data_allcom[variables2]) %>% mutate_if(is.numeric, list(function(x) round(x, 3)))
anova(gam_toutes, gam_toutes2, test = "Chisq")

AIC(gam_toutes)
AIC(gam_toutes2)
```

# Visualisation des liens entre variablesOn garde le modele sans l'annee en aleatoire.

```{r}
plot(gam_toutes)

par(mfrow = c(2,2))
mgcv::gam.check(gam_toutes)
```

## Imputation
##0.07 % de valeurs abérantes détectés (plus grand que 50) et 0.02 % plus grand que 100
```{r}
adultdata1$fitted <- exp(predict(gam_toutes, adultdata1_minmaxed %>% 
                                   filter(!is.na(RR)) %>% 
                                   mutate(Year = as.numeric(as.character(Year))) %>% 
                                   mutate_if(is.numeric, list(min_max))))

# View(adultdata1 %>% filter(is.na(fitted)))
summary(adultdata1$fitted)
boxplot(adultdata1$fitted)
boxplot(adultdata1$fitted[adultdata1$fitted <= 60])
mean(adultdata1$fitted > 60, na.rm = T)

id_outliers <- adultdata1$fitted >= 60
sum(id_outliers)
prop.table(id_outliers %>% table)

id_outliers2 <- adultdata1$fitted >100
sum(id_outliers2)
prop.table(id_outliers2 %>% table)

adultdata1 %>% filter(fitted <= 60) %>% 
  ggplot(aes(commune, fitted, col = commune)) + geom_boxplot() + 
  xlab("observed") + theme_minimal() + 
  ggtitle("Fitted values", subtitle = "for all commune") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + 
  facet_wrap(~Year, scales = "free")

adultdata1 %>% filter(commune %in% c("BANDRELE", "MTSAMBORO")) %>% filter(Year!=2022)%>%
  # group_by(Year, Week, commune) %>% summarise(fitted = mean(fitted), .groups = "drop") %>%
  ggplot(aes(Date, fitted, col = commune)) + geom_line() + 
  xlab("Week") + theme_minimal() + 
  ggtitle("Fitted values", subtitle = "") + 
  facet_wrap(~Year, scales = "free")

# graphe sans DA
adultdata1 %>% filter(commune %in% c("BANDRELE", "MTSAMBORO"), fitted <= 100) %>% 
  # group_by(Year, Week, commune) %>% summarise(fitted = mean(fitted), .groups = "drop") %>%
  ggplot(aes(Date, fitted, col = commune)) + geom_line() + 
  xlab("observed") + theme_minimal() + 
  ggtitle("Fitted vs observed", subtitle = "for all commune") + 
  facet_wrap(~Year, scales = "free")

adultdata1 %>% filter(commune %in% c("BANDRELE", "CHIRONGUI"), fitted <= 100) %>%
  # group_by(Year, Week, commune) %>% summarise(fitted = mean(fitted), .groups = "drop") %>% 
  ggplot(aes(Date, fitted, col = commune)) + geom_line() + 
  xlab("observed") + theme_minimal() + 
  ggtitle("Fitted vs observed", subtitle = "for all commune") + 
  facet_wrap(~Year, scales = "free")

## On groupe par semaine,commune et annee et moyenne
p_all <- adultdata1 %>% #filter(commune %in% c("BANDRELE", "CHIRONGUI")) %>%
  group_by(Year, Week, commune) %>% summarise(fitted = mean(fitted), .groups = "drop") %>% 
  ggplot(aes(Week, fitted, col = commune)) + geom_line() + 
  xlab("Week") + theme_minimal() + 
  ggtitle("Fitted values", subtitle = "for all commune") + 
  facet_wrap(~Year, scales = "free")

plotly::ggplotly(p_all)

adultdata1[c("Year", "Date", "commune", variables2)] %>% filter(commune %in% c("BANDRELE"), Year == 2022)

coefs <- coefficients(gam_toutes)
coefs[grepl("MRR", names(coefs))]
```
### Comportement de la moyenne et de la variance après dispersion

### Comportement de la moyenne et de la variance après dispersion

```{r}
# Moyenne et ecart-type de nombre de contacts
adultdata1%>% filter(fitted <= 60) %>% summarise_at("fitted", list(mean = function(x) mean(x, na.rm = TRUE), 
                                               sd = function(x) sd(x, na.rm = TRUE)))

```

##

```{r}
adultdata1%>%filter(!is.na(Num_adults)) %>%filter(Year!=2022) %>%ggplot(aes(Week,Num_adults,col="observed")) + geom_line(aes(Week, fitted,col="fitted")) + geom_line()  + facet_wrap(~Year)
```

```{r}
adultdata1 %>% filter(fitted < 100)%>%filter(!is.na(Num_adults)) %>%filter(Year!=2022) %>%ggplot(aes(Week,Num_adults,col="observed")) + geom_line(aes(Week, fitted,col="fitted")) + geom_line()  + facet_wrap(~Year)
```

  
```{r}
adultdata1 %>% filter(fitted < 100)%>%filter(!is.na(Num_adults)) %>%filter(commune == "MAMOUDZOU") %>%
  ggplot() + geom_line(aes(Week, Num_adults), col = "red") +
  geom_line(aes(Week, fitted), col = "blue")+
xlab("Week") +
  ylab("Fitted (red)  vs Observed (blue)")
```



## Ratio computing

$$R = \frac{d_n - d_{n-1}}{d_{max} - d_{min}}$$

$$R_i = \frac{d_i - d_{min}}{\textrm{threshold} - d_{min}}I_{x\leq \textrm{threshold}} + I_{x\geq \textrm{threshold}}$$
##Ratio=max
```{r}
get_ratio <- function(x, method = 1, threshold = NULL){
  n <- length(x)
  
  if (is.null(threshold)) threshold = max(x)
  
  if (n <= 1) {
      stop("x should be of length greater than 1!")
    } else {
    return(ifelse(x <= threshold, (x-min(x))/(threshold-min(x)), 1))
  }
}

plot(get_ratio(1:10, threshold = NULL))
```

## Ratio computing: method 2
```{r}
adultdata1_ratio <- adultdata1 %>% #filter(fitted <= 60) %>% 
  group_by(Year, Week, commune) %>% summarise(fitted = mean(fitted), .groups = "drop")


reconstitution <- adultdata1_ratio %>% 
  filter(Week %in% 1:52) %>% filter(Year != 2022) %>% filter(Year != 2020)%>% 
  group_by(Year, commune, Week) %>% 
  summarise(fitted = mean(fitted), .groups = "drop") %>% 
  mutate(Ratio = get_ratio(fitted, threshold = 60)) %>% 
  ggplot(aes(as.factor(Week), commune, fill = Ratio)) + geom_tile() + 
  scale_fill_gradient2(low = "green", mid = "orange", high = "red", midpoint = 0.5) + 
  facet_wrap(~Year, ncol = 2) + theme_minimal() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) 

plotly::ggplotly(reconstitution)

reconstitution4 <- adultdata1_ratio %>% 
  filter(Week %in% 1:53) %>% filter(Year == 2020) %>% 
  group_by(Year, commune, Week) %>% 
  summarise(fitted = mean(fitted), .groups = "drop") %>% 
  mutate(Ratio = get_ratio(fitted, threshold = 60)) %>% 
  ggplot(aes(as.factor(Week), commune, fill = Ratio)) + geom_tile() + 
  scale_fill_gradient2(low = "green", mid = "orange", high = "red", midpoint = 0.5) + 
  facet_wrap(~Year, ncol = 2) + theme_minimal() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) 

plotly::ggplotly(reconstitution4)
```


# Ratio 
```{r}
adultdata1_ratio <- adultdata1 %>% #filter(fitted <= 60) %>% 
  group_by(Year, Week, commune) %>% summarise(fitted = mean(fitted), .groups = "drop")


reconstitution <- adultdata1_ratio %>% filter(Year != 2022) %>% 
  group_by(Year, commune, Week) %>% 
  summarise(fitted = mean(fitted), .groups = "drop") %>% 
  mutate(Ratio = get_ratio(fitted, threshold = max(fitted))) %>% 
  ggplot(aes(as.factor(Week), commune, fill = Ratio)) + geom_tile() + 
  scale_fill_gradient2(low = "green", mid = "orange", high = "red", midpoint = 0.5) + 
  facet_wrap(~Year, ncol = 2) + theme_minimal() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) 

plotly::ggplotly(reconstitution)
```


## Carte avec  seuill donc on enleve les valeurs abérantes
```{r warning=FALSE, message=FALSE}
adultdata2 <- myt_map_commune %>% select(commune) %>% left_join(adultdata1_ratio, by = "commune") %>% 
  mutate(Ratio = get_ratio(fitted, threshold = 40))

lapply(2018, function(year){
  p <- adultdata2 %>% filter(Year == year) %>%filter(Week %in% 1:52) %>% ggplot() + geom_sf(aes(fill = Ratio)) + theme_map() + facet_wrap(~Week, nrow = 4) + 
scale_fill_gradient2(low = "green", mid = "orange", high = "red", midpoint = 0.5)
    p
})
```

```{r}

  p <- adultdata2 %>% filter(Year == 2018) %>%filter(Week %in% 1:52) %>% ggplot() + geom_sf(aes(fill = Ratio)) + theme_map(base_size = 9, base_family = "") + facet_wrap(~Week, nrow = 5, ncol= 11) + 
scale_fill_gradient2(low = "green", mid = "orange", high = "red", midpoint = 0.5)
    p
```


##
```{r warning=FALSE, message=FALSE}
library(tmap)
lapply(2021, function(year){
  tm_object <- tm_shape(adultdata2 %>% filter(Year == year)%>%filter(Week %in% 1:52)) +
    tm_polygons(col = "Ratio", midpoint = 0.3, title = paste0("Ratio\n(", year, ")"), palette = "seq") +
    tm_layout(aes.palette = list(seq = "-RdYlGn")) +
    tm_facets(by = "Week")
  tm_object
})
```


## Ratio

$$R_i = \begin{cases}(x_i-\min(x))/s & \text{if}\; x_i \leq s\\1 & \text{else}\end{cases} = 1+\left(\frac{x_i}{s - \min(x)}-1\right)I_{\{x_i\leq s\}}.$$

Where $s$ is the threshold (Ex: s = 63 mosquitoes) and fitted is the predicted number of mosquitoes in the commune at a given week or day.

```{r}
adultdata1[c("commune", "Date", "Year", "Num_adults", "fitted", variables2)] %>% 
  filter(commune %in% c("BANDRELE"), Week %in% 10:20, Year == 2019, fitted > 50)
```
### Summary

```{r}
summary_out <- adultdata1[id_outliers, variables] %>% 
  lapply(summary) %>% bind_rows() %>% 
  mutate(Variable = variables, .before = "Min.")

summary_in <- adultdata1[!id_outliers, variables] %>% 
  lapply(summary) %>% bind_rows() %>% 
  mutate(Variable = variables, .before = "Min.")

summary_out %>% flextable() %>% autofit() %>% theme_box()
summary_in %>% flextable() %>% autofit() %>% theme_box()
```

---------------------------OTHERS PRELIMINARIES--------

## Logistic GAM 
```{r}
# df_logistic <- adultdata1 %>% 
#   mutate(Num_adults = ifelse(Num_adults >= 10, 1, 0) %>% factor())
# 
# 
# # logistic GAM
# logistic_GAM <- mgcv::gam(fmla, data = df_logistic %>% 
#                             filter(!is.na(Num_adults)), 
#                           method = "REML", family = binomial(), select = TRUE)
# 
# summary(logistic_GAM)
# # coef(logistic_GAM)
# 
# 
# df_logistic$Ratio <- predict.gam(logistic_GAM, df_logistic, type = "response")
# df_logistic$Ratio. <- ifelse(df_logistic$Ratio >= 0.5, 1, 0) %>% as.numeric() 
# 
# confusionMatrix(factor(df_logistic$Ratio.), df_logistic$Num_adults, positive = "1")
```

```{r warning=FALSE, message=FALSE}
# df_logistic2 <- df_logistic %>% filter(Year != 2022) %>% 
#   group_by(Year, commune, Week) %>% 
#   summarise(Ratio = max(Ratio), .groups = "drop")
# 
# reconstitution3 <- df_logistic2 %>% 
#   ggplot(aes(as.factor(Week), commune, fill = Ratio)) + geom_tile() + 
#   scale_fill_gradient2(low = "green", mid = "orange", high = "red", midpoint = 0.5) + 
#   facet_wrap(~Year, ncol = 2) + theme_minimal() + 
#   theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
# 
# reconstitution3
# ggsave("./2. Adult_results/reconstition3_GAM_logit.png", width = 14, height = 8)
```


```{r warning=FALSE, message=FALSE}
# # Maps
# df_logistic2 <- myt_map_commune %>% select(commune) %>% left_join(df_logistic2, by = "commune")
# logit_plots <- lapply(2018:2021, function(year){
#   tm_object <- tm_shape(df_logistic2 %>% filter(Year == year)) +
#     tm_polygons(col = "Ratio", midpoint = 0.5, palette = "-viridis", title = paste0("Ratio\n(", year, ")")) + 
#     tm_facets(by = "Week")
#   # saving the plot
#   tmap_save(tm = tm_object, filename = paste0("./2. Adult_results/Reconstitution_map_LogitGAM_", year, ".pdf"))
#   tmap_save(tm = tm_object, filename = paste0("./2. Adult_results/Reconstitution_map_LogitGAM_", year, ".png"))
#   tm_object
# })
# 
# logit_plots
```

